First round comments from the Ad-hoc rewiew committee \\ (Maurik Holtrop, Kevin Giovankl, Zein-Eddine Meziani)

### 2018-09-08 eg6-letters/incoherent/adhocreview/1st_adhoc_comments.tex
Minor updates on incoherent

\item  The paper makes no mention of the initial momentum of the struck 
   nucleon, which I would expect to smear out the kinematics. It would be 
      useful for the reader to get an impression on how large this effect would 
      be. Does this explain the widths of the distributions in figure 2, or are 
      these widths dominated by detector resolution?\\
   \textcolor{blue}{We have studied this effect, we updated the paper to
      address the question. The review 
      committee members are invited to check appendix H in the analysis note 
      for more details.}

>>>>

\item  The paper makes no mention of the initial momentum of the struck 
   nucleon, which I would expect to smear out the kinematics. It would be 
      useful for the reader to get an impression on how large this effect would 
      be. Does this explain the widths of the distributions in figure 2, or are 
      these widths dominated by detector resolution?\\
   \textcolor{blue}{We have studied this effect, we updated the paper to
      address the question. Of relevance to this question, the appendix H in the analysis note 
      looks in more details into alternative kinematics to solve the issue. However,
      final results did not appear to be affected by any of the alternate choices,
      confirming the small impact of the Fermi momentum smearing.}
